\documentclass[12pt]{article}
\setlength{\headheight}{0ex}
\setlength{\headsep}{0ex}
\input{hogg_nasa}
\usepackage{url}
\pagestyle{empty}

\begin{document}
\noindent
\textbf{Daniel Foreman-Mackey} \hfill http://dfm.io
\smallskip

\paragraph{Professional Preparation:}~\\[3pt]
\begin{tabular}{llll}
\textsl{postdoctoral} & University of Washington & Astrophysics & starting
    July 2015 \\
\textsl{graduate} & New York University & Physics & PhD 2015 \\
\textsl{graduate} & Queen's University, Canada & Physics & MSc 2010 \\
\textsl{undergraduate} & McGill University & Physics & BSc 2008 \\
\end{tabular}

\paragraph{Honors \& Awards:}
$\bullet$~Sagan Postdoctoral Fellowship (starting July 2015);
$\bullet$~James Arthur Graduate Fellowship (2014, 2015);
$\bullet$~Horizon Fellowship in the Natural \& Physical Sciences (2012);
$\bullet$~Henry M. MacCracken Fellowship (2010);
$\bullet$~NSERC Undergraduate Summer Research Award (2007).

% \newcommand{\arxiv}[1]{{\textit{arXiv}:{#1}}}
\paragraph{Selected Publications:}
\begin{itemize}\setlength{\itemsep}{0pt}

\item Montet, B.~T., Morton, T.~D., {\bf Foreman-Mackey, D.}, \etal, 2015,
    \emph{Stellar and Planetary Properties of K2 Campaign 1 Candidates and
          Validation of 18 Systems, Including a Planet Receiving Earth-like
          Insolation}, \textit{Astrophys.\,J.} submitted (\arxiv{1503.07866})

\item {\bf Foreman-Mackey, D.}, Montet, B.~T., Hogg, D.~W., Morton, T.~D.,
    Wang, D., \& Sch\"olkopf, B., 2015,
    \emph{A systematic search for transiting planets in the K2 data}
    \textit{Astrophys.\,J.}, in press (\arxiv{1502.04715})

\item Barclay, T., Endl, M.,  Huber, D., {\bf Foreman-Mackey, D.}, \etal, 2014,
    \emph{Radial Velocity Observations and Light Curve Noise Modeling Confirm
          That Kepler-91b is a Giant Planet Orbiting a Giant Star},
    \textit{Astrophys.\,J.}, \textbf{800}, 46 (\arxiv{1408.3149})

\item {\bf Foreman-Mackey, D.}, Hogg, D.~W., \& Morton, T.~D., 2014,
    \emph{Exoplanet population inference and the abundance of Earth analogs
          from noisy, incomplete catalogs},
    \textit{Astrophys.\,J.}, \textbf{795}, 64 (\arxiv{1406.3020})

\item Dawson, R.~I., Johnson,  J.~A., Fabrycky, D.~C.,
    {\bf Foreman-Mackey, D.}, \etal, 2014,
    \emph{Large Eccentricity, Low Mutual Inclination: The Three-dimensional
          Architecture of a Hierarchical System of Giant Planets}
    \textit{Astrophys.\,J.}, \textbf{791}, 89 (\arxiv{1405.5229})

\item Ambikasaran, S., {\bf Foreman-Mackey, D.}, Greengard, L., Hogg, D.~W.,
    \& O'Neil, M., 2014,
    \emph{Fast Direct Methods for Gaussian Processes} (\arxiv{1403.6015})

\item {\bf Foreman-Mackey, D.}, Hogg, D.~W., Lang, D., \& Goodman, J., 2013,
    \emph{emcee: The MCMC Hammer},
    \textit{Pubs.\,Astr.\,Soc.\,Pac.}, \textbf{125}, 306 (\arxiv{1202.3665})

\end{itemize}


\paragraph{Popular Open Source Software:}
\begin{itemize}\setlength{\itemsep}{0pt}

\item {\bf emcee} ---
    MCMC sampling in Python. Popular in astronomy; the paper has 319 citations
    as of 2015-05-12. \url{dfm.io/emcee}

\item {\bf George} ---
    Blazingly fast Gaussian processes for regression. Implemented in C++ and
    Python bindings. Joint work with applied mathematicians at NYU.
    \url{dfm.io/george}

\item {\bf triangle.py} ---
    Simple corner plots (or scatterplot matrices) in Python.
    \url{github.com/dfm/triangle.py}

\end{itemize}

\end{document}
